---
title: "Lab 3"
author: "Christopher Munoz"
format: pdf
editor: visual
---

```{r}
load("StudentData.dat")
hist(covid, prob=TRUE, breaks=seq(-0.5, max(covid)+0.5, 1), main="Distribution of COVID Cases", xlab="Number of COVID Cases", col="lightblue", border="black")
lambda_covid <- mean(covid)
x_vals <- 0:max(covid)
y_vals <- dpois(x_vals, lambda=lambda_covid)
points(x_vals, y_vals, col='red', pch=19, cex=1.5)
lines(x_vals, y_vals, col='red', lwd=3)
legend("topright", legend=paste0("Poisson(λ = ", round(lambda_covid, 2), ")"), col="red", lwd=3)
cat("COVID: Poisson(λ =", round(lambda_covid, 2), ")\n")
```

The variable covid is best modeled by a is best modeled by a random\
variable **Poisson because our data is discrete, non-negative and represents the count of independent rare events. Poisson is also a natural choice for biological phenomenon, as my colleague says, its the "fish" distribution.**

```{r}
load("StudentData.dat")
hist(GPA, prob=TRUE, breaks=20, main="Distribution of GPA", xlab="GPA", col="lightgreen", border="black")
mean_gpa <- mean(GPA)
sd_gpa <- sd(GPA)
x_vals <- seq(min(GPA), max(GPA), length=200)
y_vals <- dnorm(x_vals, mean=mean_gpa, sd=sd_gpa)
lines(x_vals, y_vals, col='red', lwd=3)
legend("topleft", legend=paste0("Normal(μ = ", round(mean_gpa, 2), ", σ = ", round(sd_gpa, 2), ")"), col="red", lwd=3)
cat("GPA: N(μ =", round(mean_gpa, 2), ", σ =", round(sd_gpa, 2), ")\n")
```

The variable GPA is best modeled by a **Normal** random variable\
because **GPA is a continuous metric that results from averaging many independent events(assignments, tests, homework). From the Central Limit Theorem we know when many independent factors combine we get a Normal distribution.**

```{r}
load("StudentData.dat")
hist(rent, prob=TRUE, breaks=20, main="Distribution of Monthly Rent", xlab="Rent ($)", col="lightyellow", border="black")
rate_rent <- 1 / mean(rent)
x_vals <- seq(min(rent), max(rent), length=200)
y_vals <- dexp(x_vals, rate=rate_rent)
lines(x_vals, y_vals, col='red', lwd=3)
legend("topright", legend=paste0("Exponential(λ = ", round(rate_rent, 4), ")"), col="red", lwd=3)
cat("Rent: Exp(λ =", round(rate_rent, 4), ")\n")
```

The variable rent is best modeled by a **Exponential** random variable\
because **Monthly rent is continuous and strictly positive with a right skew, its commonly for monetary values and costs associated data.**

```{r}
load("StudentData.dat")
hist(HIIT, prob=TRUE, breaks=20, main="Distribution of HIIT Proportion", xlab="Proportion of Time HR > 140", col="lightcoral", border="black")
m <- mean(HIIT)
v <- var(HIIT)
alpha_hiit <- m * (m * (1 - m) / v - 1)
beta_hiit <- (1 - m) * (m * (1 - m) / v - 1)
x_vals <- seq(0, 1, length=200)
y_vals <- dbeta(x_vals, shape1=alpha_hiit, shape2=beta_hiit)
lines(x_vals, y_vals, col='red', lwd=3)
legend("topleft", legend=paste0("Beta(α = ", round(alpha_hiit, 2), ", β = ", round(beta_hiit, 2), ")"), col="red", lwd=3)
cat("HIIT: Beta(α =", round(alpha_hiit, 2), ", β =", round(beta_hiit, 2), ")\n")
```

The variable HIIT is best modeled by a **Beta** random variable\
because **High Intensity interval training represents a proportion, in this case the fraction of workouts with heart rates above 140 bmp. Since proportions are bounded between 0 and 1, the Beta distribution is the the best fit.\
\
\
\
\
\
\
\
Summary Statistics for each distribution and dataset:\
**

```         
=== SUMMARY STATISTICS ===

COVID:
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
    0.0     1.0     1.0     1.6     2.0     6.0 
Mean: 1.6 
Variance: 1.366834 
SD: 1.169117 

GPA:
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
  2.381   2.967   3.208   3.195   3.413   3.912 
Mean: 3.195423 
Variance: 0.09702458 
SD: 0.3114877 

RENT:
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
  703.3   828.3   948.5   951.1  1069.2  1196.3 
Mean: 951.103 
Variance: 20668.04 
SD: 143.7638 

HIIT:
   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
0.01157 0.10490 0.18417 0.20504 0.27874 0.70344 
Mean: 0.205038 
Variance: 0.01461413 
SD: 0.1208889
```
