% !TEX TS-program = pdflatexmk
\documentclass[12pt]{amsart}

%\usepackage[parfill]{parskip}    % Activate to begin paragraphs with an empty line rather than an indent

\usepackage[margin=1in]{geometry}

\usepackage{amsmath,amssymb,amsthm,latexsym,graphicx}
\usepackage[normalem]{ulem}
\usepackage{setspace} %used for doublespacing, etc.
\usepackage{hyperref}
\usepackage{cancel}
\usepackage[dvipsnames,usenames]{color}
\usepackage[all]{xy}
\usepackage{fancyhdr}
\pagestyle{fancy}
	\renewcommand{\headrulewidth}{0.5pt} % and the line
	\headsep=1cm
	
\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}

%Some useful environments.
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[theorem]{Example}
\newtheorem{axiom}{Axiom}
\theoremstyle{remark}
\newtheorem{remark}{Remark}
\newtheorem*{exercise}{Exercise}%[section]

%Some shortcuts helpful for our assignments
\newcommand{\bx}{\begin{exercise}}
\newcommand{\ex}{\end{exercise}}

%Some useful shortcuts for our favorite sets of numbers.
%Note, you can use these WITHOUT entering math mode
\def\RR{\ensuremath{\mathbb R}} 
\def\NN{\ensuremath{\mathbb N}}
\def\ZZ{\ensuremath{\mathbb Z}}
\def\QQ{{\ensuremath\mathbb Q}}
\def\CC{\ensuremath{\mathbb C}}
\def\EE{{\ensuremath\mathbb E}}

%Some useful shortcuts for formatting lists
\newcommand{\bc}{\begin{center}}
\newcommand{\ec}{\end{center}}
\newcommand{\be}{\begin{enumerate}}
\newcommand{\ee}{\end{enumerate}}
\newcommand{\bi}{\begin{itemize}}
\newcommand{\ei}{\end{itemize}}

%Some useful shortcuts for formatting mathematical symbols
\newcommand{\ol}[1]{\overline{#1}}
\newcommand{\oimp}[1]{\overset{#1}{\iff}} %labeled iff symbol
\newcommand{\bv}[1]{\ensuremath{ \vec{\mathbf{#1}}} } %makes a vector.
\newcommand{\mc}[1]{\ensuremath{\mathcal{#1}}} %put something in caligraphic font
\newcommand{\normale}{\trianglelefteq}
\newcommand{\normal}{\triangleleft}

%Code for formatting the proofs a little nicer for submitted homework
\makeatletter
\renewenvironment{proof}[1][\proofname]{\par\doublespacing
  \pushQED{\qed}%
  \normalfont \topsep6\p@\@plus6\p@\relax
  \list{}{%
    \settowidth{\leftmargin}{\itshape\proofname:\hskip\labelsep}%
    \setlength{\labelwidth}{0pt}%
    \setlength{\itemindent}{-\leftmargin}%
  }%
  \item[\hskip\labelsep\itshape#1\@addpunct{:}]\ignorespaces
}{%
  \popQED\endlist\@endpefalse
  \singlespacing
}
\makeatother


%Commenting tools for the professor
\newcommand{\mpg}[1]{\marginpar{ #1}} %to put comments in margins
\usepackage{soul}
\definecolor{highlight}{rgb}{1,0.6,0.6}
\sethlcolor{highlight}
\newcommand{\hlm}[1]{\colorbox{highlight}{$\displaystyle #1$}}
\newtheoremstyle{mycomment}{\topsep}{-0in}{\small \itshape \sffamily}{}{\small \itshape\sffamily}{:}{.5em}{}
\theoremstyle{mycomment}
\newtheorem*{acomment}{\color{BrickRed}{Comment}}
\newcommand{\com}[1]{{\color{OliveGreen}\begin{acomment}{#1} %#2 \color{black} 
\end{acomment}\noindent}}
\newcommand{\red}[1]{{\color{BrickRed} #1}}
\newcommand{\blue}[1]{{\color{MidnightBlue}#1}}
\newcommand{\green}[1]{{\color{OliveGreen}#1}}
\newcommand{\mwrong}[2]{\red{\cancel{#1}}\green{#2}}
\newcommand{\wrong}[2]{\red{\sout{#1}}\green{#2}}
\definecolor{OliveGreen}{rgb}{.3,.5,.2}
\definecolor{MidnightBlue}{rgb}{.3,.4,.6}
\newcommand{\pts}[1]{\hfill\blue{{#1}/5}}

\chead{MATH 265F}
\pagestyle{fancy}
%Modify these items:
\rhead{\emph{Christopher Munoz}}
\lhead{\emph{HW \#14 --- 4/10/24}}

\begin{document}

\thispagestyle{fancy}

%§14.1 1, 3, 4, 12, 13.
\section*{Section 14.1}
Show that the two given sets have equal cardinality by describing a bijection from one to the other. Describe your bijection with a formula (not as a table).
\begin{exercise}[1] $\RR$ and $(0,\infty)$.
\begin{proof}[Solution]
	We need to show bijectivity from $\RR$ and $(0, \infty)$. Consider the function $f(a) = e^a$. We observe that $f(a) = f(b)$ implies that $e^a = e^b$ and that taking the natural log of both sides gives $a = b$. This demonstrates the function injective. Because $b \in (0, \infty)$ and $f(\ln{(b)} = b$, the function is is surjective. Thus $\RR$ and $(0,\infty)$ have equal cardinality.
\end{proof}
\end{exercise}

\begin{exercise}[3] $\RR$ and $(0,1)$.
\begin{proof}[Solution]
	Let $f(a) = \frac{1}{1+e^{a}}$. Observe that $f(a) = f(b)$ implies $\frac{1}{1+e^{a}} = \frac{1}{1+2^{b}}$. Cross-multiplying both sides gives $1 + e^{a} = 1 + e^{b}$, so $e^a = e^b$. Taking the natural log of both sides gives $a = b$. Thus $f$ is injective. Let $a \in (0, \infty)$ and $b = \frac{1}{1+e^a}$. Solving for $e^a$ gives $e^a = \frac{1-b}{b}$. Taking the natural log of both sides gives $a = \ln{(\frac{1-b}{b})}$ which will always be greater than 0 as $a \in (0, 1)$ and $a \in \RR$. This demonstrates that $f$ is surjective. Thus $f$ is bijective and $\RR$ and $(0, 1)$ share the same cardinality.
\end{proof}
\end{exercise}

\begin{exercise}[4] The set of even integers and the set of odd integers.
\begin{proof}
	Let $A = \{2k: k \in \ZZ\}$ and $B = \{2n+1:n \in \ZZ \}$. Lets define our function $f: A \rightarrow B$ by $f(x) = x+1$. Suppose $f(x) = f(y)$. Then $x + 1 = y + 1$, so $x = y$. Thus $f$ is injective. Let $x = 2k \in \ZZ$, then $f(x) = f(2k) = 2k+1 = y$. Thus $f$ is surjective. Therefore $f$ is bijective and the set of even and odd integers share the same cardinality.
\end{proof}
\end{exercise}

\begin{exercise}[12] $\NN$ and $\ZZ$ (SuggestionL: use Exercise 18 from \S12.2.)
\begin{proof}[Solution]
Lets define our function $f : \NN \rightarrow \ZZ$ by 
\begin{align*}
  f(x) = \begin{cases} \frac{x}{2} & \text{if x is even,} \\ -\frac{n-1}{2} & \text{if n is odd}  \end{cases}
\end{align*}
Consider the cases where both are even, both are odd or one is even and one is odd. Suppose $x$ and $y$ are even, then $\frac{x}{2} = \frac{y}{2}$. $x = y$.
Suppose $x$ and $y$ are odd, then $-\frac{x - 1}{2} = -\frac{y - 1}{2}$, so $x - 1 = y - 1$ meaning $x = y$. Suppose $x$ is even and $y$ is odd, then $\frac{x}{2} = -\frac{y - 1}{2}$. This leads to a contradiction as the left is non-negative and the right is negative unless we choose $x = 0$ and $y = 1$ in order to make both sides equal $0$ which is unique. Thus $f$ is injective. Since our even values $n = 2k$ maps to $k \geq 0$ and odd values $n = 2k + 1$ maps to $-k \leq 0$, the integers are all mapped. Thus $f$ is surjective meaning $f$ is bijective, $\NN$ and $\ZZ$ share the same cardinality.
\end{proof}
\end{exercise}

\begin{exercise}[13] $\mc P(\NN)$ and $\mc P(\ZZ)$. (Suggestion: use Exercise 12, above.)
\begin{proof}
  Define function $f: P(\NN) \rightarrow P(\ZZ)$ by $$f(A) = \{g(n): n \in \AA\}$$ where our $g(n)$ is the function from our previous exercise, proven to be bijective. If $f(A_1) = f(A_2)$, then $\{g(n):n \in A_1\} = \{g(n):n \in A_2\}$. Since we've shown $g$ was injective, $A_1 = A_2$ and $f$ is injective. For any $B \subseteq \ZZ$, let $ A = \{n \in \NN:g(n) \in B\}$. Then $f(A) = B$, since $g$ was proven to be surjective, $f$ has to be too in our case. Thus $f$ is bijective and $P(\NN)$ and $P(\ZZ)$ share the same cardinality.
\end{proof}
\end{exercise}

%§14.2 1, 2, 7.
\section*{Section 14.2}
\begin{exercise}[1] Prove that the set $A=\{\ln(n):n\in \NN\}\subseteq \RR$ is countably infinite.
\begin{proof}
The elements of the set can be written as an infinite list of $$\ln(1)\rightarrow\ln(2)\rightarrow\ln(3)\cdots$$. Thus $A$ is countably infinite.
\end{proof}
\end{exercise}

\begin{exercise}[2] Prove that the set $A=\{(m,n)\in\NN\times\NN:m\le n\}$ is countably infinite.
\begin{proof}
We need to show that A={(m,n)∈N×N:m≤n}A = \{ (m, n) \in \mathbb{N} \times \mathbb{N} : m \leq n \}A = \{ (m, n) \in \mathbb{N} \times \mathbb{N} : m \leq n \}
 is countably infinite. First, observe that for each n∈Nn \in \mathbb{N}n \in \mathbb{N}
, the pair (n,n)∈A(n, n) \in A(n, n) \in A
, so ( A ) is infinite. To show ( A ) is countable, define a function f:A→Nf: A \to \mathbb{N}f: A \to \mathbb{N}
 by ordering pairs such that $f(m,n)=(m+n−2)(m+n−1)2+mf(m, n) = \frac{(m + n - 2)(m + n - 1)}{2} + mf(m, n) = \frac{(m + n - 2)(m + n - 1)}{2} + m$
 for$ m≤nm \leq nm \leq n$
. Suppose $f(m1,n1)=f(m2,n2)f(m_1, n_1) = f(m_2, n_2)f(m_1, n_1) = f(m_2, n_2)$
. Since this is the Cantor pairing function restricted to m≤nm \leq nm \leq n
, each pair ( (m, n) ) maps to a unique natural number. Thus, ( f ) is injective. For any k∈Nk \in \mathbb{N}k \in \mathbb{N}
, there exists a pair ( (m, n) ) with m≤nm \leq nm \leq n
 such that f(m,n)=kf(m, n) = kf(m, n) = k
, as the pairing function covers all natural numbers when extended to N×N\mathbb{N} \times \mathbb{N}\mathbb{N} \times \mathbb{N}
. Thus, ( f ) is surjective. Since ( f ) is bijective and ( A ) is infinite, ( A ) is countably infinite.


\end{proof}
\end{exercise}

\begin{exercise}[7] Prove or disprove: The set $\QQ^{100}$ is countably infinite.
\begin{proof}
Write your answer here.
\end{proof}
\end{exercise}

%§14.3 1, 3, 7.
\section*{Section 14.3}
\begin{exercise}[1] Suppose $B$ is an uncountable set and $A$ is a set. Given that there is a surjective function $f:A\to B$, what can be said about the cardinality of $A$?
\begin{proof}[Solution]
Write your answer here.
\end{proof}
\end{exercise}


\begin{exercise}[3] Prove or disprove: If $A$ is uncountable, then $|A|=|\RR|$.
\begin{proof}
Write your answer here.
\end{proof}
\end{exercise}

\begin{exercise}[7] Prove or disprove: If $A\subseteq B$ and $A$ is countably infinite and $B$ is uncountable, then $B-A$ is uncountable.
\begin{proof}
Write your answer here.
\end{proof}
\end{exercise}



%§14.4 1, 2.
\section*{Section 14.4}
\begin{exercise}[1] Show that if $A\subseteq B$ and there is an injection $g:B\to A$, then $|A|=|B|$.
\begin{proof}
Write your answer here.
\end{proof}
\end{exercise}

\begin{exercise}[2] Show that $|\RR^{2}|=|\RR|$. Suggestion: Begin by showing $|(0,1)\times(0,1)|=|(0,1)|$.
 \begin{proof}
Write your answer here.
\end{proof}
\end{exercise}


%Reflection Problem
\section*{Reflection}
\begin{exercise}[Reflection Problem] \ 

\begin{proof}[Answers] \ \\
\begin{description}
\item[How long did it take you to complete each problem?]
\item[What was easy?]
\item[What was challenging? What made it challenging?]
\item[What did you learn from comparing your answers to those in the book?]
\end{description}
\end{proof}
\end{exercise}.









 \end{document} 
