% !TEX TS-program = pdflatexmk
\documentclass[12pt]{amsart}

%\usepackage[parfill]{parskip}    % Activate to begin paragraphs with an empty line rather than an indent

\usepackage[margin=1in]{geometry}

\usepackage{amsmath,amssymb,amsthm,latexsym,graphicx}
\usepackage[normalem]{ulem}
\usepackage{setspace} %used for doublespacing, etc.
\usepackage{hyperref}
\usepackage{cancel}
\usepackage[dvipsnames,usenames]{color}
\usepackage[all]{xy}
\usepackage{fancyhdr}
\pagestyle{fancy}
	\renewcommand{\headrulewidth}{0.5pt} % and the line
	\headsep=1cm
	
\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}

%Some useful environments.
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[theorem]{Example}
\newtheorem{axiom}{Axiom}
\theoremstyle{remark}
\newtheorem{remark}{Remark}
\newtheorem*{exercise}{Exercise}%[section]

%Some useful shortcuts for our favorite sets of numbers
\newcommand{\RR}{\ensuremath{\mathbb R}} %Note, you can use these WITHOUT entering math mode
\newcommand{\NN}{\ensuremath{\mathbb N}}
\newcommand{\ZZ}{\ensuremath{\mathbb Z}}
\newcommand{\QQ}{{\ensuremath\mathbb Q}}
\newcommand{\CC}{\ensuremath{\mathbb C}}
\newcommand{\EE}{{\ensuremath\mathbb E}}
\newcommand{\PP}{{\ensuremath\mathbb P}}

%Some useful shortcuts for formatting lists
\newcommand{\bc}{\begin{center}}
\newcommand{\ec}{\end{center}}
\newcommand{\be}{\begin{enumerate}}
\newcommand{\ee}{\end{enumerate}}
\newcommand{\bi}{\begin{itemize}}
\newcommand{\ei}{\end{itemize}}

%Some useful shortcuts for formatting mathematical symbols
\newcommand{\ol}[1]{\overline{#1}}
\newcommand{\oimp}[1]{\overset{#1}{\iff}} %labeled iff symbol
\newcommand{\bv}[1]{\ensuremath{ \vec{\mathbf{#1}}} } %makes a vector.
\newcommand{\mc}[1]{\ensuremath{\mathcal{#1}}} %put something in caligraphic font
\newcommand{\mpg}[1]{\marginpar{ #1}} %to put comments in margins
\newcommand{\bsl}[1]{\texttt{\symbol{92}{\em #1}}} %for backslashes.
\newcommand{\normale}{\trianglelefteq}
\newcommand{\normal}{\triangleleft}

%Commenting tools --- You can ignore these, but if you have a question about latex and send me your source file, I'll use them to explain stuff to you.
\usepackage{soul}
\definecolor{highlight}{rgb}{1,0.6,0.6}
\sethlcolor{highlight}
\newcommand{\hlm}[1]{\colorbox{highlight}{$\displaystyle #1$}}
\newtheoremstyle{mycomment}{\topsep}{-0in}{\small \itshape \sffamily}{}{\small \itshape\sffamily}{:}{.5em}{}
\theoremstyle{mycomment}
\newtheorem*{acomment}{\color{BrickRed}{Comment}}
\newcommand{\com}[1]{{\color{OliveGreen}\begin{acomment}{#1} %#2 \color{black} 
\end{acomment}\noindent}}
%\newcommand{\com}[1]{{\color{BrickRed}{\\ Comment:}\color{OliveGreen}{#1} \\}}
\newcommand{\red}[1]{{\color{BrickRed} #1}}
\newcommand{\blue}[1]{{\color{MidnightBlue}#1}}
\newcommand{\green}[1]{{\color{OliveGreen}#1}}
\newcommand{\mwrong}[2]{\red{\cancel{#1}}\green{#2}}
\newcommand{\wrong}[2]{\red{\sout{#1}}\green{#2}}
\definecolor{OliveGreen}{rgb}{.3,.5,.2}
\definecolor{MidnightBlue}{rgb}{.3,.4,.6}
\newcommand{\pts}[1]{\hfill\blue{{#1}/5}}

\chead{MATH F265}
\pagestyle{fancy}
%Modify these items:
\rhead{\emph{Christopher Munoz}}
\lhead{\emph{HW \#4 --- 2/12/2025}}


\begin{document}

\thispagestyle{fancy}
\setstretch{2.5} %Use for 2.5 spacing
%\doublespacing %Use for double spacing

\textbf{Write the following in English Sentences. Say whether they are true or false.}
\begin{exercise}[2.7.1] $\forall x \in \RR, x^2 > 0$ \newline 
For all x in the real numbers, $x^2$ is greater than 0. \newline
This is false, for example if we let $x = 0$, then $x > 0$.
\end{exercise}
\begin{exercise}[2.7.2] $\forall x \in \RR, \exists n \in \NN, x^n \geq 0$ \newline
	For all x in the real numbers, there exists an n in the natural numbers such that $x^n \geq 0$. \newline
	This is true, if we let $n = 2$ then any x will be above or equal to zero.
\end{exercise}
\begin{exercise}[2.7.3] $\exists a \in \RR, \forall x \in \RR, ax=x$ \newline
	There exists a real number a, such that for all real numbers x, $ax = x.$ \newline
	This is true, if we let $a = 1$ then $ax = 1x = x$.
\end{exercise}
\begin{exercise}[2.7.4] $\forall X \in \mathcal{P} (\NN), X \subseteq \RR$ \newline
	For all X in the powerset of the natural numbers, X is a subset of the Real Numbers. \newline
	This is a true statement because every subset of the natural numbers is a subset of the real numbers.
\end{exercise}
\textbf{For the following, we're just staying whether its true or false.}
\begin{exercise}[2.7.5] $\forall n \in \NN, \exists X \in \mathcal{P} (\NN), |X| = n $ \newline
	True
\end{exercise}
\begin{exercise}[2.7.6] $\exists n \in \NN, \forall X \in \mathcal{P} (\NN),$ \newline
	False
\end{exercise}
\begin{exercise}[2.7.7] $\forall X \subseteq \NN, \exists n \in \ZZ, |X| = n$ \newline
	False
\end{exercise}
\begin{exercise}[2.7.8] $\forall n \in \ZZ, \exists X \subseteq \NN, |X| = n$ \newline
	False
\end{exercise}
\begin{exercise}[2.7.9] $\forall n \in \ZZ, \exists m \in \ZZ, m = n +5$ \newline 
	True
\end{exercise}
\begin{exercise}[2.7.10] $\exists m \in \ZZ, \forall n \in \ZZ, m = n+5$ \newline
True
\end{exercise}
\textbf{For these we are translating sentences into logic}
\begin{exercise}[2.9.1] if $f$ is a polynomial and its degree is greater than 2, then $f'$ is not constant.
	P: $f$ is a polynomial \newline
	Q: $f$ has a degree greater than 2 \newline
	R: $f'$ is constant \newline
	Translation: (P $\land$ Q) $\Rightarrow \neg$ R
\end{exercise}
\begin{exercise}[2.9.4]  For every prime number $p$, there is another prime number $q$ with $q > p.$ \newline
	Let $\PP$ be the set of prime numbers. \newline
	Translation: $\forall p \in \PP, \exists q \in \PP, q > p$  
\end{exercise} \singlespacing
\begin{exercise}[2.9.6] For every positive number $\varepsilon$, there is a positive number $M$ for which \newline $|f(x) - b| < \varepsilon, $ whenever $x > M.$ 

\setstretch{2.5} %Use for 2.5 spacing
	Translation: $\forall \varepsilon \in \RR, \varepsilon > 0, \exists M \in \RR, M > 0, (x > M) \Rightarrow (|f(x) - b | < \varepsilon)$
\end{exercise}
\setstretch{2.5} %Use for 2.5 spacing
\begin{exercise}[2.9.7] There exists a real number $a$ for which $a + x = x$ for every real number x.
	Translation: $\exists a \in \RR, \forall x \in \RR, a + x = x$
\end{exercise}
\textbf{For the following we are negating each statement}
\begin{exercise}[2.10.2] If $x$ is prime, then $\sqrt{x}$ is not a rational number. \newline
	Negation: If $x$ is not a prime number, then $\sqrt{x}$ is a rational number.
\end{exercise}
\begin{exercise}[2.10.3] For every prime number $p$, there is another prime number $q$ with $q > p$. \newline
	Negation: There exists a prime number $p$  such that $q \leq p$ for all other prime numbers $q$.
\end{exercise}
\begin{exercise}[2.10.6] There exists a real number $a$ for which $a + x = x$ for every real number $x$. \newline
	Negation: For all real numbers $a$, there exists a real number $x$ such that $a + x \neq x$
\end{exercise}
\begin{exercise}[2.10.8] If $x$ is a rational number and $x \neq 0$, then $\tan{(x)}$ is not a rational number. \newline
	Negation: There exists a rational number x that is non-zero such that $\tan{(x)}$ is a rational number.
\end{exercise}
\singlespacing
\begin{exercise}[2.10.10] If $f$ is a polynomial and its degree is greater than 2, then $f'$ is not constant. \newline
\newline
Negation: If $f$ is a polynimal and its degree is less than or equal to 2, then $f'$ is constant.
\end{exercise}
\setstretch{2.5}
\textbf{Reflection Reflection Reflection}\newline
How long did it take?
It took around 1 to 2 minutes to do each problems including the practice problems, the part of the assignment that took the most time was setting up LaTeX using the template, but once it was setup it was pretty smooth sailing. \newline

What was easy for you? Pretty much everything we covered in class, with some of the problems "rhyming" with what we have already covered. \newline

What was challenging? Problem 4 in section 2.7 since I wasn't entirely sure if something like {1,2} is a subset of the real numbers, the fact that its a list tripped me up a bit, but I figured if we took the hypothetical powerset of the real numbers then {1,2} would be in there. Might be bad logic and I'll find out when this is graded if its good or bad logic. \newline

Comparison. Some of my answers are different, but I think they are logically equivalent, something about the way the solution to problem 1 in section 2.9 rubs me the wrong way because they set R to "$f'$ is not constant" so the "not" is embedded in R. In software there is this concept called encapsulation, I'm not a huge fan of encapsulation,  rather I much prefer composition.
\end{document}
 \end

  
